---
title: "Challenge: Complex Nested"
teaching: 1
exercises: 10
---

::::::::::: questions ::::::::::

## Questions

 - Which method do you prefer?

::::::::::::::::::::::::::::::::



:::::::::::::::::: challenge

## You try it again!

Create the following nested challenge using [`<div>`](03-div-challenge-blocks.html) tags, [{dovetail}](04-dovetail-challenge-blocks.html), and [fenced divs](05-fenced-div-challenge-blocks.html):

Please place your answers in [this answer sheet](files/challenge-file.Rmd) and
use the same text editor you would normally use for editing Carpentries lesson
materials.

::::::::::::::::::::::::::::


::::::::::::::::::::::::::::::::::::::::: challenge

## Challenge

Use the `paste()` function to concatenate the strings "hello" and "there" in R

::::::::::::::::::::: solution

## School Solution

```{r}
paste("hello", "there")
```

::::::::::::::::::::::::::::::

Great! Now use `paste0()` to paste together "mono" and "rail" to make "monorail"

::::::::::::::::::::: solution

## Fast Solution

```{r}
paste0("mono", "rail")
```

:::::::::::::::::::::::::::::::
::::::::::::::::::::::::::::::::::::::::::::::::::

