---
title: "Results for HISWH21"
---

## HTML `<div>`

<div class="challenge">

  ## Challenge
  
  Use the `paste()` function to concatenate the strings “hello” and “there” in R.
  
  <div class="solution">
  
    ## Solution
    
    ```r
    paste("hello","there")
    ```
    
    ```output
    [1] "hello there"
    ```
  </div>

</div>

## {dovetail}

```{r setup-1, include=FALSE}
library(dovetail)
```

```{challenge}
  
#' ## Challenge
#'
#' Use the `paste()` function to concatenate the strings “hello” and “there” in R.
#'
#' @solution Solution
#'
#' ```r
paste("hello","there")
#' ```
#'    
#' ```output
[1] "hello there"
#' ```
```

## pandoc fenced div

::::::::::::::::::::::::::::::::::::::::::::: challenge
  
## Challenge

Use the `paste()` function to concatenate the strings “hello” and “there” in R.

:::::::::::::::::::::: solution

## Solution

```r
paste("hello","there")
```
    
```output
[1] "hello there"
```
::::::::::::::::::::::

:::::::::::::::::::::::::::::::::::::::::::::

--------------------------------------------------------------------------------

## HTML `<div>`

<div class="challenge">

  ## Challenge
  
  Use the `paste()` function to concatenate the strings “hello” and “there” in R.
  
  <div class="solution">
  
    ## School Solution
    
    ```r
    paste("hello","there")
    ```
    
    ```output
    [1] "hello there"
    ```
  </div>
  
  Great! Now use `paste0()` function to paste together "mono" and "rail" to make "monorail"
  
    <div class="solution">
  
    ## Fast Solution
    
    ```r
    paste0("mono","rail")
    ```
    
    ```output
    [1] "monorail"
    ```
  </div>

</div>

## {dovetail}

```{r setup-2, include=FALSE}
library(dovetail)
```

```{challenge}
  
#' ## Challenge
#'
#' Use the `paste()` function to concatenate the strings “hello” and “there” in R.
#'
#' @solution School Solution
#'
#' ```r
paste("hello","there")
#' ```
#'    
#' ```output
[1] "hello there"
#' ```
#'
#'Great! Now use `paste0()` function to paste together "mono" and "rail" to make "monorail"
#' @solution Fast Solution
#'    
#' ```r
paste0("mono","rail")
#' ```
#'   
#' ```output
[1] "monorail"
#' ```
```

## pandoc fenced div

## pandoc fenced div

::::::::::::::::::::::::::::::::::::::::::::: challenge
  
## Challenge

Use the `paste()` function to concatenate the strings “hello” and “there” in R.

:::::::::::::::::::::: solution

## School Solution

```r
paste("hello","there")
```
    
```output
[1] "hello there"
```
::::::::::::::::::::::

Great! Now use `paste0()` function to paste together "mono" and "rail" to make "monorail"

:::::::::::::::::::::: solution

## Fast Solution

```r
paste0("mono","rail")
```

```output
[1] "monorail"
```
::::::::::::::::::::::

:::::::::::::::::::::::::::::::::::::::::::::

