---
title: "Results for blawh95"
---

# Challenge: Simple Nested

Please write your answers for the simple nested challenge below

## HTML `<div>`

<div class="challenge">

## Challenge

Use the `paste()` function to concatenate the strings “hello” and “there” in R

<div class="solution">

## Solution

```r
paste("hello", "there")
```

```output
## [1] "hello there"
```

</div>
</div>

## {dovetail}

```{r setup, include=FALSE}
library(dovetail)
```

```{challenge}
#' ## Challenge
#'
#' Use the `paste()` function to concatenate the strings “hello” and “there” in R
#'
#' @solution Solution
#'
#' ```r
paste("hello", "there")
#' ```
#'
#' ```output
"hello there"
#' ```
```

## pandoc fenced div

::: challenge

## Challenge

Use the `paste()` function to concatenate the strings “hello” and “there” in R

:::::: solution

## Solution

```r
paste("hello", "there")
```

```output
## [1] "hello there"
```

::::::

:::

--------------------------------------------------------------------------------


# Challenge: Complex Nested

Please write your answers for the complex nested challenge below

## HTML `<div>`

<div class="challenge">

## Challenge

Use the `paste()` function to concatenate the strings “hello” and “there” in R

<div class="solution">

## School Solution

```r
paste("hello", "there")
```

```output
## [1] "hello there"
```

</div>

Great! Now use `paste0()` to paste together “mono” and “rail” to make “monorail”

<div class="solution">

## Fast Solution

```r
paste0("mono", "rail")
```

```output
## [1] "monorail"
```

</div>
</div>

## {dovetail}

```{r setup, include=FALSE}
library(dovetail)
```

```{challenge}
#' ## Challenge
#'
#' Use the `paste()` function to concatenate the strings “hello” and “there” in R
#'
#' @solution School Solution
#'
#' ```r
paste("hello", "there")
#' ```
#'
#' ```output
"hello there"
#' ```
#'
#' @end
#'
#' Great! Now use `paste0()` to paste together “mono” and “rail” to make “monorail”
#'
#' @solution Fast Solution
#'
#' ```r
paste0("mono","rail")
#' ```
#'
#' ```output
"monorail"
#' ```
```

## pandoc fenced div

::: challenge

## Challenge

Use the `paste()` function to concatenate the strings “hello” and “there” in R

:::::: solution

## School Solution

```r
paste("hello", "there")
```

```output
## [1] "hello there"
```

::::::

Great! Now use `paste0()` to paste together “mono” and “rail” to make “monorail”

:::::: solution

## Fast Solution

```r
paste0("mono", "rail")
```

```output
## [1] "monorail"
```

::::::

:::

