---
title: "Results for knibe84"
---

# Challenge: Simple Nested

Please write your answers for the simple nested challenge below

## HTML `<div>`

<div class='challenge'>

## Challenge

Use the `paste()` function to concatenate the strings “hello” and “there” in R

## Solution

<div class='solution'>
```r
paste("hello", "there")
```

</div>
</div>

## {dovetail}

```{r setup-1, include=FALSE}
library(dovetail)
```

```{challenge}
#' ## Challenge
#' 
#' Use the `paste()` function to concatenate the strings “hello” and “there” in R
#' 
#' @solution Solution
#' ```r
paste("hello", "there")
#' ```
#'
#' ```output
[1] "hello there"
#' ```
```

## pandoc fenced div

::::::::::::::::::::::::::::::::::::::::::: Challenge

## Challenge

Use the `paste()` function to concatenate the strings “hello” and “there” in R

:::::::::::::::::::::::: solution

## Solution
```r
paste("hello", "there")
```

```output
[1] "hello there"
```
:::::::::::::::::::::::
:::::::::::::::::::::::::::::::::::::::::::

--------------------------------------------------------------------------------

# Challenge: Complex Nested

Please write your answers for the complex nested challenge below

## HTML `<div>`

<div class='challenge'>

## Challenge

Use the `paste()` function to concatenate the strings “hello” and “there” in R

## Solution

<div class='solution'>
```r
paste("hello", "there")
```

Great! Now use `paste0()` to paste together “mono” and “rail” to make “monorail”

<div class='solution'>
```r
paste0("mono", "rail")
```

</div>
</div>

## {dovetail}

```{r setup-2, include=FALSE}
library(dovetail)
```

```{challenge}
#' ## Challenge
#' 
#' Use the `paste()` function to concatenate the strings “hello” and “there” in R
#' 
#' @solution Solution
#' ```r
paste("hello", "there")
#' ```
#' Great! Now use `paste0()` to paste together “mono” and “rail” to make “monorail”
#' 
#' @solution Solution
#' ```r
paste0("mono", "rail")
#' ```

```

## pandoc fenced div

::::::::::::::::::::::::::::::::::::::::::: Challenge

## Challenge

Use the `paste()` function to concatenate the strings “hello” and “there” in R

:::::::::::::::::::::::: solution

## Solution
```r
paste("hello", "there")
```

::::::::::::::::::::::::

Great! Now use `paste0()` to paste together “mono” and “rail” to make “monorail”

:::::::::::::::::::::::: solution

## Solution
```r
paste0("mono", "rail")
```

::::::::::::::::::::::::
:::::::::::::::::::::::::::::::::::::::::::
