---
title: "Results for halgr54"
---

# Challenge: Simple Nested

Please write your answers for the simple nested challenge below

## HTML `<div>`

<div class='challenge'>

Use the `+` operator to concatenate the strings "hello " and "there" in R

<div class='solution'>

## Solution

```R
paste("hello", "there")
```

```output
"hello there"
```
</div>
</div>


## {dovetail}
```{r setup-1, include = FALSE}
library(dovetail)
```
```{challenge}
#' ## Challenge
#'
#' U
#' Use the `+` operator to concatenate the strings "hello " and "there" in R
#' @solution Solution
#'
#' ```R
paste("hello", "there")
#' ```
#' ```output
"hello there"
#' ```
```

## pandoc fenced div

::::::::::::::::::::::::::::::::::::::::::::: challenge

## Challenge

Use the `+` operator to concatenate the strings "hello " and "there" in R

:::::::::::::::::::::: solution

## solution

```R
paste("hello", "there")
```

```output
"hello there"
```

::::::::::::::::::::::::::::::
::::::::::::::::::::::::::::::::::::::::::::::::::::::::
--------------------------------------------------------------------------------

# Challenge: Complex Nested

Please write your answers for the complex nested challenge below

## HTML `<div>`

<div class='challenge'>

Use the `+` operator to concatenate the strings "hello " and "there" in R

<div class='solution'>

## Solution

```R
paste("hello", "there")
```

```output
"hello there"
```
</div>

Great! Now use `paste0()` to paste together “mono” and “rail” to make “monorail”

<div class='solution'>

## Solution

```R
paste0("mono", "rail")
```

```output
"monorail"
```
</div>

</div>


## {dovetail}
```{r setup-2, include = FALSE}
library(dovetail)
```
```{challenge}
#' ## Challenge
#'
#' Use the `+` operator to concatenate the strings "hello " and "there" in R
#' @solution Solution
#'
#' ```R
paste("hello", "there")
#' ```
#' ```output
"hello there"
#' ```
#' @end
#'
#' Great! Now use `paste0()` to paste together “mono” and “rail” to make “monorail”
#'
#' @solution Solution
#'
#' ```R
paste0("mono", "rail")
#' ```
#' ```output
"monorail"
#' ```
```

## pandoc fenced div

::::::::::::::::::::::::::::::::::::::::::::: challenge

## Challenge

Use the `+` operator to concatenate the strings "hello " and "there" in R

:::::::::::::::::::::: solution

## solution

```R
paste("hello", "there")
```

```output
"hello there"
```

::::::::::::::::::::::::::::::

Great! Now use `paste0()` to paste together “mono” and “rail” to make “monorail”


:::::::::::::::::::::: solution

## solution

```R
paste0("mono", "rail")
```

```output
"monorail"
```

::::::::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::::::::::::::::::::::
